\documentclass[14pt]{beamer}

%-------------------------------------------------
%   THEMES & PACKAGES
%-------------------------------------------------
\usepackage{graphicx}

%-------------------------------------------------
%   TITLE
%-------------------------------------------------
\title{Software Development Project}
\subtitle{Progress Report}
\date{June 20, 2016}
\author{Jose Mayoral, Octavio Arriaga, Minh Nguyen}

%-------------------------------------------------
%   BEGIN
%-------------------------------------------------
\begin{document}

%-------------------------------------------------
\maketitle

%-------------------------------------------------
%   Features
%-------------------------------------------------
\begin{frame}{The multi\_map\_navigation Package}
    \begin{alertblock}{Features}
        \begin{itemize}
            \item Switching between multiple maps
            \item Wormhole feature for traversal between maps
            \item Elevator Manager for transitions
        \end{itemize}
    \end{alertblock}
\end{frame}

%-------------------------------------------------
%   Integration
%-------------------------------------------------
\begin{frame}{Integration}
    \begin{alertblock}{Integration with ROS}
        The package can be launched as a ROS node
    \end{alertblock}
    \begin{alertblock}{Integration with robocup repository}
    \begin{itemize}
        \item run with move\_base
        \item reuses environment yaml files from the robocup repository
    \end{itemize}
    \end{alertblock}
\end{frame}

%-------------------------------------------------
%   Memory model
%-------------------------------------------------
\begin{frame}{Memory model}
    \begin{alertblock}{MongoDB}
        \begin{itemize}
            \item The maps are stored in a local MongoDB server
            \item Adding map can be done in RVIZ by launching the map setting launch file and the corresponding rviz configuration file in the package.
            \item Uses the map\_store package to load maps into mongodb server.
            \item Maps are loaded as YAML file linking to the PNG map image and specifying the map dimensions.
        \end{itemize}
    \end{alertblock}
\end{frame}

\begin{frame}{Requirements}
    \begin{alertblock}{Maps in Mongodb}
        \begin{itemize}
            \item Initialize Mongo database
        		\item Maps must be loading before (not mapping just navigation).
            \item $map\_setting$ launch file provided by $multi\_map\_navigation$ node.
            \item Load maps to the server using yaml.
		\end{itemize}       
	\end{alertblock}
\end{frame}

\begin{frame}{Limitations}
    \begin{alertblock}{General Limitations}
        \begin{itemize}
            \item Definition File with declared wormholes.
            \item Environments must be mapped before.
            \item Wormholes must be added by hand.
        \end{itemize}
    \end{alertblock}
\end{frame}

\begin{frame}{Used Nodes}
    \begin{alertblock}{$Multi\_Map\_Navigation$}
        \begin{itemize}
        \item $mongo\_wrapper\_ros: $ Interface ROS and Mongo.
        \item $elevator\_manager:$ Manages transitions between maps.
        \end{itemize}
    \end{alertblock}
\end{frame}

\begin{frame}{Used Nodes (2)}
    \begin{alertblock}{$map\_store$}
        \begin{itemize}
        		\item $map\_manager:$ Server which initialize and manages services related to maps:
        		\begin{itemize}
        			\item $list\_maps$
        			\item $publish\_maps$
        			\item $delete\_map$
        			\item $rename\_map$
        			\item $dynamic\_map$
        			\item $set\_origin$
        		\end{itemize}
        \end{itemize}
    \end{alertblock}
\end{frame}

\begin{frame}{Used Nodes (3)}
    \begin{alertblock}{$move\_base$}
    		\begin{itemize}
    		    			\item $map\_server: $ loads a map and get a costmap using the next listed node.
    			\item $costmap\_2d: $ giving an image from $map_server$ and a reference frame it converts a map to costmap.
    			\item $amcl$ giving costmap and reference and child frame it computes robot localization.

    			\item $fake\_localization$, $global\_planner$ and $dwa\_local\_planner$, etc are involved as well but they work after.
        \end{itemize}
    \end{alertblock}    
\end{frame}

\begin{frame}{Problems?}
	\begin{center}
		\LARGE \textsc{\textbf{A LOT!!!!!!!!!!!!!!!!}}	
	\end{center}
\end{frame}

\begin{frame}{Current Status}
    \begin{alertblock}{Pending}
    		\begin{itemize}
		\item Costmap conversion is not working properly.
		\item Test Navigation.
        \end{itemize}   
    \end{alertblock}
\end{frame}

%-------------------------------------------------
%   END
%-------------------------------------------------
\end{document}
